Deep Probabilistic Models for Camera Geo-Calibration

### 2018-09-20 chapters/mcmc/paper.tex
changes in mcmc

Proportional to the probability distribution of the camera parameters,
$f(\Theta; \mathbf{C})$, the scoring function, $S(\Theta;
\mathbf{C})$, is defined as a linear combination of multiple constraint
functions:
%
\begin{equation}
  S(\Theta; \mathbf{C}) = \sum_{}{w_i g(c_i, \Theta)} \propto
  f(\Theta; \mathbf{C}),
\end{equation}
%
where $w_i$ is a weight and $g(c_i, \Theta)$ is a constraint function
which is larger if the calibration, $\Theta$, is more consistent with
the image information, $c_i$. While the exact set of constraints
depends on the image and database contents, we define a variety of
% scott review
functions in our implementation, including geometric configuration of
multiple weak correspondences, constraints on geographic location, and
priors over the field of view and camera orientation. 
%
We focus on the first
constraint, the latter are simple Gaussian and uniform distributions.

@@

We proposed an MCMC-based approach framework for single image camera
geo-calibration which leverages a large geographic database. Our
results demonstrate the superiority of our method versus several
baseline methods, without requiring nearby ground-level imagery as is
typical for most vision techniques. For future work, we will explore
methods for integrating approaches which use image-based matching.

>>>>

Proportional to the probability distribution of the camera parameters,
$f(\Theta; \mathbf{C})$, the scoring function, $S(\Theta;
\mathbf{C})$, is defined as a linear combination of multiple constraint
functions:
%
\begin{equation}
  S(\Theta; \mathbf{C}) = \sum_{}{w_i g(c_i, \Theta)} \propto
  f(\Theta; \mathbf{C}),
\end{equation}
%
where $w_i$ is a weight and $g(c_i, \Theta)$ is a constraint function
which is larger if the calibration, $\Theta$, is more consistent with
the image information, $c_i$. 
%
While the scoring function can take any type of constraint functions,
we define a variety of functions in our implementation, including
geometric configuration of multiple weak correspondences, constraints
on geographic location, and priors over the field of view and camera
orientation, to demonstrate the performance of our model. 
%
%While the exact set of constraints
%depends on the image and database contents, we define a variety of
%functions in our implementation, including geometric configuration of
%multiple weak correspondences, constraints on geographic location, and
%priors over the field of view and camera orientation. 
%
We focus on the first constraint specifically, the latter are simple
Gaussian and uniform distributions.

@@

We proposed an MCMC-based approach framework for single image camera
geo-calibration which leverages a large geographic database. Our
results demonstrate the superiority of our method versus several
baseline methods, without requiring nearby ground-level imagery as is
typical for most vision techniques.
While we applied only a small set of primitive constraints in this work,  
the proposed framework is able to take any kind of constraints.
In the following chapters, we will explore to develop more sophisticated
constraint functions.
